\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-03-09 paper/wireframe/wireframe.tex
added preliminary suppositions

\section{Preliminary Suppositions \& Implications}
Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications. The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation. Depending on the aims and objectives of your study, describe how the anticipated results will impact future scholarly research, theory, practice, forms of interventions, or policymaking. Note that such discussions may have either substantive [a potential new policy], theoretical [a potential new understanding], or methodological [a potential new way of analyzing] significance.

>>>>

\section{Preliminary Suppositions \& Implications}
\begin{itemize}
    \item A lot of research appears to be out of date in the field of lock security.
    \item This research will cover Carrier/Lenel's particular implementation of BLE, which to the Author's knowledge has not been tested in an academic enviornment before.
    \item This research will extend the Wiegand research of prior by attacking newer hardware with better security features.
    \item This research has the potential to potentially affect the future design of locks from the Carrier/Lenel brand, in addition to removing security vulnerabilities in future revisions of the product.
    \item This research will provide a baseline for future work in evaluating locks from different vendors
\end{itemize}
#Just because you don't have to actually conduct the study and analyze the results, doesn't mean you can skip talking about the analytical process and potential implications. The purpose of this section is to argue how and in what ways you believe your research will refine, revise, or extend existing knowledge in the subject area under investigation. Depending on the aims and objectives of your study, describe how the anticipated results will impact future scholarly research, theory, practice, forms of interventions, or policymaking. Note that such discussions may have either substantive [a potential new policy], theoretical [a potential new understanding], or methodological [a potential new way of analyzing] significance.
